---
output: html_document
---
Exploring Red Wine Quality by Xinlin Feng
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.
library(ggplot2)
library(dplyr)
library(GGally)
library(scales)
library(memisc)
library(reshape)
library(gridExtra)
# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
wine_dataset <- read.csv('wineQualityReds.csv')
```
####In This report, by using the statistical program R, I will explore a data set called "wineQualityReds" which content is on wine quality and physicochemical propertise. My purpose is to find which chemical properties has influence on the quality of red wines.
####The description of this data set:
https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt

# Data Summary
```{r echo=FALSE, Data_summary}
str(wine_dataset)
summary(wine_dataset)
```
####There are 1599 entries, each has 13 variables; 
####My priciple interests are about the quelity of wine, so I will have a specificate look at the quality part:
```{r echo=FALSE, Quality_summary}
summary(wine_dataset$quality)
```
####Wine quality is a discrete variable range from 1 - 10, and the mean of it is 5.636, the median is 6.00.
####format quality by id "X":
```{r echo=FALSE, message=FALSE, warning=FALSE, Data_format}
wine_dataset$X = factor(wine_dataset$X)
table(wine_dataset$quality)

wine_dataset$quality <- factor(wine_dataset$quality, ordered = T)
str(wine_dataset$quality)
```
# Univariate Plots Section
### Examine the structure of this data set.
####Naively, first thing come to my mind is to have a plot about the distribution of each variable: 
```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_1}
univariate_plot_c <- function(x, xlabel) {
  return (ggplot(aes(x = x), data = wine_dataset) +
            geom_histogram(aes(x = x, ..density..)) +
            geom_density(aes(x = x, ..density..)) +
            xlab(xlabel) +
            ylab("count")
          )
}
univariate_plot_d <- function(x, xlabel) {
  return (qplot(data = wine_dataset, x = x,
                geom = 'bar',
                xlab = xlabel, ylab = 'count'))
}
univariate_plot_c(wine_dataset$fixed.acidity, 'fixed acidity')
summary(wine_dataset$fixed.acidity)
univariate_plot_c(wine_dataset$volatile.acidity, 'volatile acidity')
summary(wine_dataset$volatile.acidity)
univariate_plot_c(wine_dataset$sulphates, 'sulphates')
summary(wine_dataset$sulphates)
univariate_plot_c(wine_dataset$alcohol, 'alcohol')
summary(wine_dataset$alcohol)
univariate_plot_c(wine_dataset$free.sulfur.dioxide, 'free sulfur dioxide')
summary(wine_dataset$free.sulfur.dioxide)
univariate_plot_c(wine_dataset$total.sulfur.dioxide, 'total sulfur dioxide')
summary(wine_dataset$total.sulfur.dioxide)

```

####Fixed and volatile acidity, sulphates, alcohol and sulfur dioxides, likely to be a long-tailed distribution.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_2}
univariate_plot_c(wine_dataset$citric.acid, 'cirtic acid')
summary(wine_dataset$citric.acid)

```
####Citric acid appeared to have a large number of zero values in this distribution
.
```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_3}
univariate_plot_c(wine_dataset$residual.sugar, 'residual sugar')
summary(wine_dataset$residual.sugar)

univariate_plot_c(wine_dataset$chlorides, 'chlorides')
summary(wine_dataset$chlorides)


```

####Residual sugar and chlorides have extreme outliers in its distribution

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_4}
univariate_plot_c(wine_dataset$density, 'density')
summary(wine_dataset$density)
univariate_plot_c(wine_dataset$pH, 'pH')
summary(wine_dataset$pH)

```

####Density and pH are normally distributed, with few outliers. the shape is very clear.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_5}
univariate_plot_d(wine_dataset$quality, 'quality')
summary(wine_dataset$quality)
```

####Although only have 5 discrete bars here, quality is in a normal distribution shape.

# Univariate Analysis

### What is the structure of your dataset?
####-As I mentioned above, there are 1599 entries, each has 13 variables, and it is labeled by "X".
####-it seems that density and pH are normally distributed, with few outliers.
####-Fixed and volatile acidity, sulfur dioxides, sulphates, and alcohol seem to be long-tailed.
####-Residual sugar and chlorides have extreme outliers.
####-Citric acid appeared to have a large number of zero values. 


### What is/are the main feature(s) of interest in your dataset?
#### -I'm pretty interseted in the quality of the wine, although it is ranged from 3 - 8 only, I can find that it is more or less a normal distribution.  A large majority of the wines examined received ratings of 5 or 6, and very few received 3, 4, or 8.
#### -Finally, my goal is digging that which factor has what kind of related to quality of wine.


### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?

####I will combine all "acid" factors together." Because I suspect the different acid concentrations might alter the taste of the wine. 

### Did you create any new variables from existing variables in the dataset?
####I instantiated an ordered factor, rating, classifying each wine sample as 'bad', 'fair', or 'excellent'.
```{r echo=FALSE, create_1}
#create a new variable 'rating'
wine_dataset$rating <- ifelse(wine_dataset$quality < 5, 'bad', ifelse(
  wine_dataset$quality < 7, 'fair', 'excellent'))
wine_dataset$rating <- ordered(wine_dataset$rating,
                     levels = c('bad', 'fair', 'excellent'))
summary(wine_dataset$rating)

qplot(wine_dataset$rating)
```

####Also, fixed.acidity, volatile.acidity and citric.acid are different types of acids; I created a combined variable, TAC.acidity, containing the sum of tartaric, acetic, and citric acid.

```{r echo=FALSE, message=FALSE, warning=FALSE, create_2}
wine_dataset$TAC.acidity <- wine_dataset$fixed.acidity + wine_dataset$volatile.acidity + wine_dataset$citric.acid

univariate_plot_c(wine_dataset$TAC.acidity, "TAC acidty")
```

####TAC acidity is formed by 3 kinds of acid, and it is a long-tailed distribution.

### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?

#### Yes, Citric.acid stood out from other distributions. It had an irregularly looking distribution which hard to tell the relation between quality of wine and this variable.

####I transformed the acids to log10 scale, add have the plot to see its log10 distributions, because I wish to see if it matches the shape of distribution in 'PH'

```{r echo=FALSE, message=FALSE, warning=FALSE, Transform_acids}
ggplot(data = wine_dataset,
       aes(x = fixed.acidity)) +
  geom_density(aes(x = fixed.acidity, ..density..)) +
  geom_histogram(aes(x = fixed.acidity, ..density..)) +
  scale_x_log10()

ggplot(data = wine_dataset,
       aes(x = volatile.acidity)) +
  geom_density(aes(x = volatile.acidity , ..density..)) +
  geom_histogram(aes(x = volatile.acidity , ..density..)) +
  scale_x_log10()

ggplot(data = wine_dataset,
       aes(x = citric.acid)) +
  geom_density(aes(x = citric.acid, ..density..)) +
  geom_histogram(aes(x = citric.acid, ..density..)) +
  scale_x_log10()

```

####It shows that fixed.acidity and volatile.acidity appear to be normally-distributed in log10 scale. By definition, PH is a measure of acidity and is on a logarithmic scale, thus it matches wiht our transform. However, citric.acid does not appear to be normally-distributed on log10 scale.

```{r echo=FALSE, Zero_entry}
length(subset(wine_dataset, citric.acid == 0)$citric.acid)
```
####There are 132 entries with a value of zero. This yields some concerns on whether or not these 132 values were reported or not valid, considering that the next 'bin' higher contains only 32 observations.

####Also, for some variables such as "residual.sugar", "chlorides" and "sulphates", all of them are kind long tailed, I truncated them at 95% and take a log10 scale transform. 

```{r echo=FALSE, message=FALSE, warning=FALSE, turncated}
p1 <- ggplot(data = wine_dataset, aes(x = residual.sugar)) +
  geom_histogram(aes(x = residual.sugar, ..density..)) +
  geom_density(aes(x = residual.sugar, ..density..)) +
  scale_x_continuous(lim = c(0, quantile(wine_dataset$residual.sugar, 0.95))) +
  xlab('residual.sugar, 95th percentile truncated')

p2 <- p1 + scale_x_log10() + xlab('residual.sugar, log10')
grid.arrange(p1, p2, ncol=1)

p1 <- ggplot(data = wine_dataset, aes(x = chlorides)) +
  geom_histogram(aes(x = chlorides, ..density..)) +
  geom_density(aes(x = chlorides, ..density..)) +
  scale_x_continuous(lim = c(0, quantile(wine_dataset$chlorides, 0.95))) +
  xlab('chlorides, 95th percentile truncated')

p2 <- p1 + scale_x_log10() + xlab('chlorides, log10')
grid.arrange(p1, p2, ncol=1)

p1 <- ggplot(data = wine_dataset, aes(x = sulphates)) +
  geom_histogram(aes(x = sulphates, ..density..)) + 
  geom_density(aes(x = sulphates, ..density..)) +
  scale_x_continuous(lim = c(0, quantile(wine_dataset$sulphates, 0.95))) +
  xlab('sulphates, 95th percentile truncated')

p2 <- p1 + scale_x_log10() + xlab('sulphates, log10')
grid.arrange(p1, p2, ncol=1)

rm(p1, p2)

```

####In this group of plot, after 95th percentile truncated, those plots removed extreme values, and more concentrated to centern in log10 scale. 

####I also have a boxplot to provide more info about data set's distribution.

```{r echo=FALSE, Boxplot}
#define plot function:
boxplot <- function(column, ylabel) {
  return (qplot(data = wine_dataset, x = 'simple',
                y = column, geom = 'boxplot',
                xlab = '', ylab = ylabel))
}

grid.arrange(boxplot(wine_dataset$fixed.acidity, 'fixed acidity'),
             boxplot(wine_dataset$volatile.acidity, 'volatile acidity'),
             boxplot(wine_dataset$citric.acid, 'citric acid'),
             boxplot(wine_dataset$TAC.acidity, 'TAC acidity'),
             boxplot(wine_dataset$residual.sugar, 'residual sugar'),
             boxplot(wine_dataset$chlorides, 'chlorides'),
             boxplot(wine_dataset$free.sulfur.dioxide, 'free sulf. dioxide'),
             boxplot(wine_dataset$total.sulfur.dioxide, 'total sulf. dioxide'),
             boxplot(wine_dataset$density, 'density'),
             boxplot(wine_dataset$pH, 'pH'),
             boxplot(wine_dataset$sulphates, 'sulphates'),
             boxplot(wine_dataset$alcohol, 'alcohol'),
             ncol = 4)

```

####Boxplot matches the plot above shows chlorides and sulphates have a extreme tail value; acids and dioxides are long tailed; and density, pH is normal distributed.

# Bivariate Plots Section
####I have 2 groups of boxplots, the one is quality vs variable, 

```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots}
get_bivariate_boxplot <- function(x, y, ylab) {
  return(ggplot(aes(x, y), data = wine_dataset) +
           geom_jitter( alpha = .3)  +
  geom_boxplot( alpha = .5,color = 'blue') +
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4) + ylab(ylab))
}
#quality vs variables:
             get_bivariate_boxplot(wine_dataset$quality, 
wine_dataset$fixed.acidity, 'fixed acidity')
             get_bivariate_boxplot(wine_dataset$quality, wine_dataset$volatile.acidity,'volatile acidity')
             get_bivariate_boxplot(wine_dataset$quality, 
wine_dataset$citric.acid, 'citric acid')
             get_bivariate_boxplot(wine_dataset$quality, 
wine_dataset$TAC.acidity, 'TAC acidity')
             get_bivariate_boxplot(wine_dataset$quality,
log10(wine_dataset$residual.sugar), 'residual sugar')
             get_bivariate_boxplot(wine_dataset$quality, 
log10(wine_dataset$chlorides), 'chlorides')
             get_bivariate_boxplot(wine_dataset$quality, 
wine_dataset$free.sulfur.dioxide, 'free sulf. dioxide')
             get_bivariate_boxplot(wine_dataset$quality, 
wine_dataset$total.sulfur.dioxide, 'total sulf. dioxide')
             get_bivariate_boxplot(wine_dataset$quality,
wine_dataset$density, 'density')
             get_bivariate_boxplot(wine_dataset$quality, 
wine_dataset$pH, 'pH')
             get_bivariate_boxplot(wine_dataset$quality, 
log10(wine_dataset$sulphates), 'sulphates')
             get_bivariate_boxplot(wine_dataset$quality, 
wine_dataset$alcohol, 'alcohol')
```             

####Above boxplots are quality vs variables. It shows that volatile acidity, sulphates, alcohol, citric acid shows most influence on quality.
   
```{r echo=FALSE, warning=FALSE, message=FALSE, Bivariate_Plots_2}             
#rating vs variables:
             get_bivariate_boxplot(wine_dataset$rating, wine_dataset$fixed.acidity,
                                   'fixed acidity')
             get_bivariate_boxplot(wine_dataset$rating, wine_dataset$volatile.acidity,
                                   'volatile acidity')
             get_bivariate_boxplot(wine_dataset$rating, wine_dataset$citric.acid,
                                   'citric acid')
             get_bivariate_boxplot(wine_dataset$rating, wine_dataset$TAC.acidity,
                                   'TAC acidity')
             get_bivariate_boxplot(wine_dataset$rating, log10(wine_dataset$residual.sugar),
                                   'residual sugar')
             get_bivariate_boxplot(wine_dataset$rating, log10(wine_dataset$chlorides),
                                   'chlorides')
             get_bivariate_boxplot(wine_dataset$rating, wine_dataset$free.sulfur.dioxide,
                                   'free sulf. dioxide')
             get_bivariate_boxplot(wine_dataset$rating, wine_dataset$total.sulfur.dioxide,
                                   'total sulf. dioxide')
             get_bivariate_boxplot(wine_dataset$rating, wine_dataset$density,
                                   'density')
             get_bivariate_boxplot(wine_dataset$rating, wine_dataset$pH,
                                   'pH')
             get_bivariate_boxplot(wine_dataset$rating, log10(wine_dataset$sulphates),
                                   'sulphates')
             get_bivariate_boxplot(wine_dataset$rating, wine_dataset$alcohol,
                                   'alcohol')

```


####Above boxplots are rating vs variables. It confirms that volatile acidity, sulphates, alcohol, citric acid shows most influence on quality.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?
####From ploting above, it shows that generally, wines which labeled by "excellent" generally has those features:
####-Lower PH value, which correspond to lower volatile acidity;
####-Higher sulphates, higher alcohol, higher fixed acidity and higher citric acid.
####-Residual sugar, chlorides and sulfur dioxides did not seem to have a direct impact on the quality or rating of wines.  
### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

####It appears that different types of acid affect wine quality differently, fixed acidity and citiric acid seems have positive effect on quality while volatile acidity has a opposite effect, which is out of my expectation.

### What was the strongest relationship you found?
####By utilizing cor.test, I calculated the correlation for each of these variables against quality:
```{r echo=FALSE, correlation}
simple_cor_test <- function(x, y) {
  return(cor.test(x, as.numeric(y))$estimate)
}

correlations <- c(
  simple_cor_test(wine_dataset$fixed.acidity, wine_dataset$quality),
  simple_cor_test(wine_dataset$volatile.acidity, wine_dataset$quality),
  simple_cor_test(wine_dataset$citric.acid, wine_dataset$quality),
  simple_cor_test(wine_dataset$TAC.acidity, wine_dataset$quality),
  simple_cor_test(log10(wine_dataset$residual.sugar), wine_dataset$quality),
  simple_cor_test(log10(wine_dataset$chlorides), wine_dataset$quality),
  simple_cor_test(wine_dataset$free.sulfur.dioxide, wine_dataset$quality),
  simple_cor_test(wine_dataset$total.sulfur.dioxide, wine_dataset$quality),
  simple_cor_test(wine_dataset$density, wine_dataset$quality),
  simple_cor_test(wine_dataset$pH, wine_dataset$quality),
  simple_cor_test(log10(wine_dataset$sulphates), wine_dataset$quality),
  simple_cor_test(wine_dataset$alcohol, wine_dataset$quality))
names(correlations) <- c('fixed.acidity', 'volatile.acidity', 'citric.acid',
                         'TAC.acidity', 'log10.residual.sugar',
                         'log10.chlordies', 'free.sulfur.dioxide',
                         'total.sulfur.dioxide', 'density', 'pH',
                         'log10.sulphates', 'alcohol')
correlations
```
####Let's see how these variables compare, plotted against each other and faceted by wine rating:
```{r echo=FALSE, correlation_2}
ggplot(data = wine_dataset, aes(x = log10(sulphates), y = alcohol)) +
  facet_wrap(~rating) +
  geom_point(alpha = .5) 
simple_cor_test(log10(wine_dataset$sulphates), wine_dataset$alcohol)

ggplot(data = wine_dataset, aes(x = volatile.acidity, y = alcohol)) +
  facet_wrap(~rating) +
  geom_point(alpha = .5) 
simple_cor_test(wine_dataset$volatile.acidity, wine_dataset$alcohol)

ggplot(data = wine_dataset, aes(x = citric.acid, y = alcohol)) +
  facet_wrap(~rating) +
  geom_point(alpha = .5) 
simple_cor_test(wine_dataset$citric.acid, wine_dataset$alcohol)

ggplot(data = wine_dataset, aes(x = volatile.acidity, y = log10(sulphates))) +
  facet_wrap(~rating) +
  geom_point(alpha = .5) 
simple_cor_test(wine_dataset$volatile.acidity, log10(wine_dataset$sulphates))

ggplot(data = wine_dataset, aes(x = citric.acid, y = log10(sulphates))) +
  facet_wrap(~rating) +
  geom_point(alpha = .5) 
simple_cor_test(wine_dataset$citric.acid, log10(wine_dataset$sulphates))

ggplot(data = wine_dataset, aes(x = citric.acid, y = volatile.acidity)) +
  facet_wrap(~rating) +
  geom_point(alpha = .5) 
simple_cor_test(wine_dataset$citric.acid, wine_dataset$volatile.acidity)
```

####I personaly think that the quality and rating is tightly related to the alcohol(with correlate factor 0.4762) with a positive relationship, so as sulphates(0.3086) and citric acid(0.2264).
####On the other hand, volatile acidity(-0.3906) show a strong negative relationship toward the quality of wines.


# Multivariate Plots Section
###Alcohol and other variables:
####Play some multivariate about the relation between alcohol and other variables.
####First: Alcohol vs Density
```{r echo=FALSE, Multivariate_Plots_1}
ggplot(data = wine_dataset,
       aes(y = density, x = alcohol,
           color = quality)) +
  geom_point() +
  scale_color_brewer(palette = "Reds") +
  geom_smooth(method = "lm", se = FALSE, size = 1) +
  theme(panel.background = element_rect(fill = "black"))
simple_cor_test(wine_dataset$alcohol, wine_dataset$density) 
```

####Accroding to Physics, the higher density of wine, the lower persentage of alcohol(density lower than water) it should has, this plot shows this relation, but it seems that the quality of wines are more or less evenly distributed in this plot, which make some sense because on previous section, we are hard to tell the relation between density and quality. This implied me that there might be some factor else influence the density. My reasoning is that since alcohol is negtively related to density while positively related to quality, at first I expect a negtive relation between density and quality, which means that the dark reds should concentrated on down-right corner, but I can not have this on plot, this remind me of there might be some 3rd factor influence the density. I highly suspect some thing is that 3rd factor which can change the density and kind cancels the fact of alcohol. This factor also must increase the density, thus fixed acidity, sulphates, citric acid are candidates:

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_2}
ggplot(data = wine_dataset,
       aes(y = density, x = fixed.acidity,
           color = quality)) +
  geom_point() +
  scale_color_brewer(palette = "Reds") +
  geom_smooth(method = "lm", se = FALSE, size = 1) +
  theme(panel.background = element_rect(fill = "black"))

simple_cor_test(wine_dataset$fixed.acidity, wine_dataset$density)

ggplot(data = wine_dataset,
       aes(y = density, x = sulphates,
           color = quality)) +
  scale_x_continuous(limits=c(0.3,1.5)) +
  geom_point() +
  scale_color_brewer(palette = "Reds") +
  geom_smooth(method = "lm", se = FALSE, size = 1) +
  theme(panel.background = element_rect(fill = "black"))
simple_cor_test(wine_dataset$sulphates, wine_dataset$density)

ggplot(data = wine_dataset,
       aes(y = density, x = citric.acid,
           color = quality)) +
  geom_point() +
  scale_color_brewer(palette = "Reds") +
  geom_smooth(method = "lm", se = FALSE, size = 1) +
  theme(panel.background = element_rect(fill = "black"))
simple_cor_test(wine_dataset$citric.acid, wine_dataset$density)
```

####Obvious proportional relation between fixed acidity to density, also this relation shown between citric acid and density. 

```{r echo=FALSE, Multivariate_Plots_3}
ggplot(data = wine_dataset,
       aes(x = citric.acid, y = volatile.acidity,
           color = quality)) +
  geom_point() +
  facet_wrap(~rating)
simple_cor_test(wine_dataset$citric.acid, wine_dataset$volatile.acidity)

ggplot(data = wine_dataset,
       aes(x = alcohol, y = log10(sulphates),
           color = quality)) +
  geom_point() +
  facet_wrap(~rating)
simple_cor_test(log10(wine_dataset$sulphates), wine_dataset$alcohol)
```

####Volatile acidity and citric acid shows strong negative correlation here and it can see that higher quality wine are in reletively lower volatile acidity, and higher sulphates.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?
####I examined the 4 features which showed high correlation with quality. These scatterplots were a little bit crowded, thus I faceted them by rating to illustrate the population differences between wines. It's clear that a higher citric acid and lower volatile (acetic) acid contributes towards better wines. Likewise, better wines tended to have higher sulphates and alcohol content.

### Were there any interesting or surprising interactions between features?
####I surprisingly found fixed acidity and citric acid linear to density, that is a little beyond my knowledge.
### OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

------

# Final Plots and Summary

### Plot One: Effect of acids on wine quality
```{r echo=FALSE, Plot_One}
grid.arrange(ggplot(data = wine_dataset, aes(x = quality, y = fixed.acidity,
                                   fill = quality)) + 
               ylab('Fixed Acidity (g/dm^3)') +
               xlab('Quality') +
               geom_boxplot(),
             ggplot(data = wine_dataset, aes(x = quality, y = volatile.acidity,
                                   fill = quality)) +
               ylab('Volatile Acidity (g/dm^3)') +
               xlab('Quality') +
               geom_boxplot(), 
             ggplot(data = wine_dataset, aes(x = quality, y = citric.acid,
                                   fill = quality)) +
               ylab('Citric Acid (g/dm^3)') +
               xlab('Quality') +
               geom_boxplot(), 
             ggplot(data = wine_dataset, aes(x = quality, y = pH,
                                   fill = quality)) +
               ylab('pH') +
               xlab('Quality') +
               geom_boxplot())

```

### Description One
####This plot shows that higher acidity pH is more likely to be found in higher-rated wines. The presence of volatile acid negatively affected wine quality. Citric acidity had a high correlation with wine quality, while fixed acid had a smaller positive impact.

### Plot Two: Effect of Alcohol 
```{r echo=FALSE, Plot_Two}
ggplot(data = wine_dataset, aes(x = quality, y = alcohol,
                                   fill = quality)) +
               ggtitle('Alcohol vs Wine Qualities') +
               ylab('Alcohol (% volume)') +
               xlab('Quality') +
               geom_boxplot()

simple_cor_test(wine_dataset$alcohol, wine_dataset$quality)

```

### Description Two
####This plot shows the effect of alcohol content on wine quality. Generally, higher alcohol content correlated with higher wine quality. However, as the outliers and intervals show, alchol content alone can not produce a higher quality.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(data = subset(wine_dataset, rating != 'fair'),
       aes(x = volatile.acidity, y = alcohol,
                      color = rating)) +
  geom_point() +
  ggtitle('Alcohol vs. Volatile Acidity and Wine Quality') +
  xlab('Volatile Acidity (g / dm^3)') +
  ylab('Alcohol (% volume)')
```

### Description Three
####This plot is tricky, I removed "fair" rating wine, only keep 2 extreme end to tell the difference since points in plot are too crowd. As the correlation tests shown above, wine quality was affected most strongly by alcohol and volaticle acidity. It's apparent that high volatile acidity--with few exceptions--kept wine quality down. A combination of high alcohol content and low volatile acidity produced better wines.

```{r echo=FALSE, nothing}
```
------

# Reflection

####Mainly speaking: The struggles I meet in this report is that I found that those quality is a subjective measure by expert, after bunch of plots, it shows alcohol content, sulphates, and acidity, is important to wine quality, the correlations for these variables are within reasonable fluctuation. The graphs adequately illustrate the factors that make good wines 'good' and bad wines 'bad'. 
####Further in future, since I found that there are 4 factors can strongly influence the quality of wines, a deeper look at weather those 4 factors are independent or correlated is planed. 
